lawn
=======

```{r echo=FALSE}
knitr::opts_chunk$set(
  comment = "#>",
  collapse = TRUE,
  warning = FALSE,
  message = FALSE
)
```

[![cran checks](https://cranchecks.info/badges/worst/lawn)](https://cranchecks.info/pkgs/lawn)
[![R-check](https://github.com/ropensci/lawn/workflows/R-check/badge.svg)](https://github.com/ropensci/lawn/actions?query=workflow%3AR-check)
[![codecov.io](https://codecov.io/github/ropensci/lawn/coverage.svg?branch=master)](https://codecov.io/github/ropensci/lawn?branch=master)
[![rstudio mirror downloads](https://cranlogs.r-pkg.org/badges/lawn?color=ff69b4)](https://github.com/r-hub/cranlogs.app)
[![cran version](https://www.r-pkg.org/badges/version/lawn)](https://cran.r-project.org/package=lawn)

`lawn` is an R wrapper for the Javascript library [turf.js](https://turfjs.org/). In addition, we have a few functions to interface with the [geojson-random](https://github.com/mapbox/geojson-random) and [geojsonhint](https://www.npmjs.com/package/geojsonhint) Javascript libraries, for generating random GeoJSON objects and linting GeoJSON, respectively.

## Install

The latest release of `lawn` is available from CRAN

```{r eval=FALSE}
install.packages("lawn")
```

development version

```{r eval=FALSE}
remotes::install_github("ropensci/lawn")
```

```{r}
library("lawn")
```

## Documentation

https://docs.ropensci.org/lawn/

## Contributors

* [Scott Chamberlain](https://github.com/sckott)
* [Jeff Hollister](https://github.com/jhollist)
* [Thanh Lê](https://github.com/thanhleviet)

## Meta

* Please [report any issues or bugs](https://github.com/ropensci/lawn/issues).
* License: MIT
* Get citation information for `lawn` in R doing `citation(package = 'lawn')`
* Please note that this package is released with a [Contributor Code of Conduct](https://ropensci.org/code-of-conduct/). By contributing to this project, you agree to abide by its terms.

## Additional disclaimer
Portions of this code have been contributed by Jeff Hollister, US EPA.  As such, that code is subjec to the following disclaimer: <https://www.epa.gov/home/github-contribution-disclaimer>
